Air raids on the UK: understanding the effect of time on casualties

### 2024-12-04 paper/paper.qmd
updated

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

# Summarize the first model
modelsummary(first_model, 
             statistic = c("estimate", "std.error", "conf.low", "conf.high")

first_model <-
  readRDS(file = here::here("air-raids/models/first_model.rds"))
```

>>>>

@@

# Summarize the first model
first_model <-
  readRDS(file = here::here("models/first_model.rds"))

modelsummary(first_model, 
             statistic = c("estimate", "std.error", "conf.low", "conf.high"))

```
